Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-16 manuscript.Rmd
added a few lines

Every study that can be preregistered can also be preregistered with code.
The only difference is that PAC demands a comprehensive and complete analysis plan.
With traditional preregistration, researchers are able to omit details and get away with decisions that are made only after having seen the data, thus, potentially biasing statistical results.
Some researchers may not feel ready to decide on every detail of the analysis plan before data collection.
In such cases, we recommend making decisions based on the best available knowledge, and if these decisions still prove infeasible, make simple assumptions and revise and explain them later as described in Section [Deviating from the preregistration and exploration] in the final manuscript.

@@

This function illustrates two advantages of PAC.
First, a PAC can easily include data-dependent decisions by creating different analysis branches under different conditions.
Second, it highlights how difficult it is to describe a statistical analysis precisely.
The same verbal descriptions may be implemented differently by different persons depending on their statistical and programming knowledge and their expectations and beliefs.
One example would be using the function `wilcox.test` instead of the combinations of the functions `rank` and `t.test`.
Either of them is a valid implementation of the Mann–Whitney–Wilcoxon test, but the first assumes equal variance.
In contrast, the second applies Welch's correction by default and hence is robust even with unequal variances across groups [@zimmermanRankTransformationsPower1993].
Mentioning every such minute implementation detail is almost impossible and would result in overly verbose preregistrations.
Still, these details can make a difference and unwanted researchers' degrees of freedom.

@@

Naturally we did not access the data when we initially wrote this code.
We therefore did not know the exact format the data would have.
This means that we did need to change our preregistration after accessing the data to include i.e. the recoding of gender (lines 17-22) and the items (lines 23-26).[^prereg-changes]

[^prereg-changes]: We invite the reader to evaluate the changes we made to the preregistered code.
Either on [GitHub](https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg...main) → "Files changed" or directly in Git with `git diff v0.0.1.1-prereg preregistration.Rmd`.

>>>>

Every study that can be preregistered and ultimately uses computer code for the statistical analysis, can also be preregistered with code.
The only difference is that PAC demands a comprehensive and complete analysis plan.
With traditional preregistration, researchers may (unintentionally) omit details and thus introduce decisions that need to be made only after having seen the data.
We emphasize again that deviations from the preregistration are not only possible but actually likely.
The advtange of PAC is that all deviations from the planned analysis as implemented in code are tracked, and the final analysis can be easily compared to the PAC.
Importantly, we see PAC as a means to increase transparency not as a means to limit researchers in their statistical analyses.
In practice, researchers may not feel ready to decide on every detail of the analysis plan before data collection.
In such cases, we recommend making decisions based on the best available knowledge, and if these decisions still prove infeasible, make simple assumptions and revise and explain them later as described in Section [Deviating from the preregistration and exploration] in the final manuscript.

@@

This function illustrates two advantages of PAC.
First, a PAC can easily include data-dependent decisions by creating different analysis branches under different conditions.
Second, it highlights how difficult it is to describe a statistical analysis precisely.
The same verbal descriptions may be implemented differently by different persons depending on their statistical and programming knowledge and their expectations and beliefs.
One example would be using the function `wilcox.test` instead of the combinations of the functions `rank` and `t.test`.
Either of them is a valid implementation of the Mann–Whitney–Wilcoxon test, but the first assumes equal variance.
In contrast, the second applies Welch's correction by default and hence is robust even with unequal variances across groups [@zimmermanRankTransformationsPower1993].
Mentioning every such minute implementation detail is almost impossible and would result in overly verbose preregistrations.
Still, these details can make a difference in the interpretation of statistical results and, thus, represent undisclosed researchers' degrees of freedom.

@@

Naturally we did not access the data when we initially wrote this code.
We therefore did not know the exact format the data would have.
This means that we did need to change our preregistration after accessing the data to include i.e. the recoding of gender (lines 17-22) and the items (lines 23-26).
We invite the reader to evaluate the changes we made to the preregistered code on [GitHub](https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b).
